CDIPS. I. Light Curves in Open Clusters from TESS Sectors 6 \& 7

### 2019-08-07 paper_I/table_cdips_targets.tex
update target table for page fit

  212898200266481408 &           NGC\_1798 &  CantatGaudin\_2018 &     212898200266481408 &   77.836762 &  47.602184 &   0.804664 &  -0.306808 &  0.079538 &        15.239067 &         16.137050 &         14.300698 &       NGC\_1798 &            NGC\_1798 &                  string\_match &      False &                                                NaN &     9.300 &         NaN \\
  436314118309711616 &         Melotte 20 &           Dias2014 &             694-021435 &   48.197155 &  48.642080 &   6.375356 &  -2.441825 &  0.571211 &        16.312990 &         16.868382 &         15.480946 &     Melotte\_20 &          Melotte\_20 &                  string\_match &      False &                                stellar association &     7.700 &         NaN \\
  441656473511397504 &         Melotte 20 &           Dias2014 &             697-023323 &   50.495676 &  49.275058 &   5.990684 &  -2.017660 &  1.224379 &        15.746423 &         16.410664 &         14.962594 &     Melotte\_20 &          Melotte\_20 &                  string\_match &      False &                                stellar association &     7.700 &         NaN \\
  441814425228579968 &         Melotte 20 &           Dias2014 &             702-024826 &   52.294234 &  50.339258 &   2.636974 &  -6.331214 &  0.612354 &        12.820641 &         13.845972 &         11.826541 &     Melotte\_20 &          Melotte\_20 &                  string\_match &      False &                                stellar association &     7.700 &         NaN \\
  534326573375563008 &      Collinder 463 &           Dias2014 &             809-006294 &   26.385454 &  71.730761 &  -2.234133 &  -0.254922 &  1.339348 &         9.017250 &          9.168780 &          8.777838 &  Collinder\_463 &       Collinder\_463 &                  string\_match &      False &                                                NaN &     8.450 &       0.066 \\
 2003032425991508224 &           ASCC 123 &           Dias2014 &             718-100888 &  339.167259 &  53.587715 &  -3.523145 &  -1.026365 &  0.080821 &        15.595959 &         16.562428 &         14.616383 &       ASCC\_123 &            ASCC\_123 &                  string\_match &      False &                                                NaN &     8.191 &         NaN \\
 2031125085568334848 &  ASCC 105,ASCC 105 &  Dias2014,Dias2014 &  587-091022,587-091016 &  295.309048 &  27.374026 &  -4.300105 &  -6.154838 &  0.134811 &        16.256998 &         17.375406 &         15.173058 &       ASCC\_105 &            ASCC\_105 &                  string\_match &      False &                                                NaN &     7.910 &         NaN \\
 2203397563780025216 &                NaN &      Zari\_2018\_UMS &    2203397563780025216 &  326.249614 &  59.270811 &   1.008246 &  -4.504666 &  2.550234 &        10.899773 &         11.129973 &         10.515632 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\
 2921370238592116224 &            ASCC 33 &           Dias2014 &             327-019044 &  106.101530 & -24.633675 &  -1.830129 &   2.907392 &  0.354147 &        15.540529 &         15.834187 &         15.075217 &        ASCC\_33 &             ASCC\_33 &                  string\_match &      False &                                                NaN &     7.700 &         NaN \\
 2944678923021117824 &                NaN &      Zari\_2018\_PMS &    2944678923021117824 &   94.221472 & -16.524928 &  -4.891108 &   5.187349 &  2.782549 &        17.017532 &         18.707790 &         15.741343 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\
 3061987330417564928 &                NaN &      Zari\_2018\_UMS &    3061987330417564928 &  111.999764 &  -1.654681 & -16.693736 &  11.698526 &  4.483383 &         9.060237 &          9.296353 &          8.706912 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\
 4468588570104961536 &      Collinder 359 &           Dias2014 &             465-071806 &  271.337344 &   2.859011 &  -6.067793 & -11.841687 &  0.222911 &        16.597385 &         17.202381 &         15.849189 &  Collinder\_359 &       Collinder\_359 &                  string\_match &      False &                                                NaN &     7.450 &         NaN \\
 5237684579941961856 &        Melotte\_105 &  CantatGaudin\_2018 &    5237684579941961856 &  170.158607 & -63.573204 &  -6.292756 &   1.531851 &  0.294776 &        14.673732 &         15.888803 &         13.571835 &    Melotte\_105 &         Melotte\_105 &                  string\_match &      False &                                                NaN &     8.375 &         NaN \\
 5517771771107237888 &      Collinder 173 &           Dias2014 &             207-016493 &  119.352691 & -48.671736 &  -4.453542 &   5.411883 &  0.362699 &        15.930569 &         16.325560 &         15.368135 &  Collinder\_173 &       Collinder\_173 &  K13\_index\_table\_string\_match &      False &  K13index: duplicated/coincides with other clus... &       NaN &         NaN \\
 5852217060603554816 &         Platais 11 &           Dias2014 &             124-103457 &  206.927830 & -65.255509 &  -6.012783 &  -1.985373 &  0.119739 &        15.898413 &         16.775694 &         14.973198 &     Platais\_11 &          Platais\_11 &  K13\_index\_table\_string\_match &      False &  K13index: possibly this is a cluster, but para... &       NaN &         NaN \\
 5867315416772454400 &         Platais 10 &           Dias2014 &             149-141566 &  210.294439 & -60.295024 &  -4.568015 &  -0.810601 &  0.368087 &        15.197055 &         15.521402 &         14.684991 &     Platais\_10 &          Platais\_10 &                  string\_match &      False &                                                NaN &     8.340 &         NaN \\
 5867551536877904640 &           NGC\_5381 &  CantatGaudin\_2018 &    5867551536877904640 &  210.348670 & -59.508581 &  -6.412219 &  -3.052808 &  0.364516 &        16.601406 &         17.142036 &         15.814178 &       NGC\_5381 &            NGC\_5381 &                  string\_match &      False &                                                NaN &     8.650 &         NaN \\
 5874572743305780480 &            ASCC\_79 &  CantatGaudin\_2018 &    5874572743305780480 &  226.986254 & -61.942703 &  -3.765162 &  -4.668764 &  0.981699 &        11.241166 &         11.451314 &         10.888834 &        ASCC\_79 &             ASCC\_79 &                  string\_match &      False &                                                NaN &     6.950 &         NaN \\
 5878616953190551168 &           NGC\_5617 &  CantatGaudin\_2018 &    5878616953190551168 &  217.533631 & -60.768071 &  -5.738512 &  -3.337642 &  0.473326 &        15.280778 &         15.662171 &         14.728349 &       NGC\_5617 &            NGC\_5617 &                  string\_match &      False &                                                NaN &     8.250 &         NaN \\
 5997629225643484416 &                NaN &      Zari\_2018\_PMS &    5997629225643484416 &  242.843543 & -37.812758 & -15.520921 & -25.141830 &  6.849145 &        14.319747 &         15.803695 &         13.119771 &            NaN &                 NaN &                           NaN &        NaN &                                                NaN &       NaN &         NaN \\

>>>>

 497093746702988672 &  2006361919000756992 &  2048442943413035776 &  5867618572762132864 \\
          Platais 3 &             ASCC 121 &           Teutsch 35 &           Loden\_1152 \\
           Dias2014 &             Dias2014 &             Dias2014 &       Kharchenko2013 \\
         799-012054 &           724-092321 &           630-074483 &            650278772 \\
            71.4458 &              337.708 &              294.081 &              209.832 \\
            69.6454 &              54.6607 &              35.8782 &             -59.2883 \\
            -5.1826 &             -3.48356 &             -3.19716 &              -3.6399 \\
          -0.478063 &             -1.28297 &             -2.04354 &             -3.93699 \\
           0.579745 &             0.196117 &             0.324896 &             0.397703 \\
            15.1735 &              15.4843 &              15.1863 &              16.4277 \\
            15.5786 &              16.3805 &              15.7505 &               16.991 \\
            14.6008 &              14.5227 &              14.4853 &              15.6807 \\
          Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
          Platais\_3 &             ASCC\_121 &             ASCC\_103 &           Loden\_1152 \\
       string\_match &         string\_match &         string\_match &         string\_match \\
              False &                False &                False &                False \\
                NaN &                  NaN &                  NaN &                  NaN \\
                8.8 &                  6.4 &                 8.39 &                8.065 \\
                NaN &                  NaN &                  NaN &                0.092 \\
